% This is a Basic Assignment Paper but with like Code and stuff allowed in it, there is also url, hyperlinks from contents included. 

\documentclass[11pt]{article}

% Preamble

\usepackage[margin=1in]{geometry}
\usepackage{amsfonts, amsmath, amssymb}
\usepackage{fancyhdr, float, graphicx}
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage{fouriernc} % Use the New Century Schoolbook font
\usepackage[nottoc, notlot, notlof]{tocbibind}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{blindtext}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,      
    urlcolor=cyan,
    pdfpagemode=FullScreen,
    }

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

% Header and Footer
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyhead[L]{\textit{\Large{Wireless Devices and Mobile Security - 3nd Year B. Tech}}}
\fancyhead[R]{\textit{Krishnaraj T}}
\fancyfoot[C]{\thepage}
\renewcommand{\footrulewidth}{1pt}



% Other Doc Editing
% \parindent 0ex
%\renewcommand{\baselinestretch}{1.5}

\begin{document}

\begin{titlepage}
    \centering

    %---------------------------NAMES-------------------------------

    \huge\textsc{
        MIT World Peace University
    }\\

    \vspace{0.75\baselineskip} % space after Uni Name

    \LARGE{
        Wireless Devices and Mobile Security\\
        Third Year B. Tech, Semester 5
    }

    \vfill % space after Sub Name

    %--------------------------TITLE-------------------------------

    \rule{\textwidth}{1.6pt}\vspace*{-\baselineskip}\vspace*{2pt}
    \rule{\textwidth}{0.6pt}
    \vspace{0.75\baselineskip} % Whitespace above the title



    \huge{\textsc{
            Installation and Configuration of Any Wifi Traffic Analyser Tool. 
        }} \\



    \vspace{0.5\baselineskip} % Whitespace below the title
    \rule{\textwidth}{0.6pt}\vspace*{-\baselineskip}\vspace*{2.8pt}
    \rule{\textwidth}{1.6pt}

    \vspace{1\baselineskip} % Whitespace after the title block

    %--------------------------SUBTITLE --------------------------	

    \LARGE\textsc{
        Lab Assignment 9
    } % Subtitle or further description
    \vfill

    %--------------------------AUTHOR-------------------------------

    Prepared By
    \vspace{0.5\baselineskip} % Whitespace before the editors

    \Large{
        Krishnaraj Thadesar \\
        Cyber Security and Forensics\\
        Batch A1, PA 10
    }


    \vspace{0.5\baselineskip} % Whitespace below the editor list
    \today

\end{titlepage}


\tableofcontents
\thispagestyle{empty}
\clearpage

\setcounter{page}{1}

\section{Aim}

\section{Objectives}


\section{Theory}
Title, Basic explanation, Need, screenshots of demonstration and conclusion. 
\section{Platform}
\textbf{Operating System}: Arch Linux x86-64 \\
\textbf{IDEs or Text Editors Used}: Visual Studio Code\\
\textbf{Compilers or Interpreters}: Python 3.10.1\\

\section{Working Screenshots}


\section{Conclusion}
Thus, the installation and configuration of Any Wifi Traffic Analyser Tool was successfully done. We installed Wireshark, captured packets and analysed them. 
\clearpage
\begin{thebibliography}{99}
    \bibitem{ciscorouters}
    Cisco Routers. \\
    Website: \url{https://www.cisco.com/c/en/us/products/routers/index.html}
  
    \bibitem{tplinkrouters}
    TP-Link Routers. \\
    Website: \url{https://www.tp-link.com/us/home-networking/wifi-router/}
  
    \bibitem{dlinkrouters}
    D-Link Routers. \\
    Website: \url{https://www.dlink.com/en/consumer/routers}
  
    \bibitem{netgearrouters}
    Netgear Routers. \\
    Website: \url{https://www.netgear.com/home/products/networking/wifi-routers/}
  
    \bibitem{asusrouters}
    ASUS Routers. \\
    Website: \url{https://www.asus.com/Networking-IoT-Servers/WiFi-Routers-Products/}
  
    \bibitem{linksysrouters}
    Linksys Routers. \\
    Website: \url{https://www.linksys.com/us/routers/}
  
    \bibitem{mikrotikrouters}
    MikroTik Routers. \\
    Website: \url{https://mikrotik.com/products/group/routers}
  
    \bibitem{ubiquitirouters}
    Ubiquiti Routers. \\
    Website: \url{https://www.ui.com/products/#routing}
  
    \bibitem{huaweirouters}
    Huawei Routers. \\
    Website: \url{https://consumer.huawei.com/en/routers/}
  \end{thebibliography}
  

\end{document}